Evolution of the AGN UV luminosity function from redshift 7.5

### 2019-05-16 Paper/paper.tex

\item
  In Model 1 we assume that the functions $F_0$, $F_1$ and $F_2$ from
  Equation~\eqref{eqn:global} are Chebyshev polynomials in
  $\left(1+z\right)$, written as
  \begin{equation}
    F_i\left(1+z\right)=\sum_{j=0}^{n_i}c_{i,j}T_j\left(1+z\right)
    \label{eqn:cbs}
  \end{equation}
  for $i\in\{0,1,2\}$, where $c_{i,j}$ are the parameters from
  Equation~\eqref{eqn:global} and $T_j\left(1+z\right)$ are Chebyshev
  polynomials of the first kind. We try successively higher orders of
  Chebyshev polynomials in order to arrive at a good fit with the
  data.  As we discuss below, we find that $\phi_*$, $M_*$ and
  $\alpha$ prefer quadratic, cubic, and linear evolutions in
  $\left(1+z\right)$, respectively.  For the faint-end slope $\beta$
  we adopt a double power law to account for a possible break at
  $z\sim 3$ that is currently not covered with credible data.  Thus we
  write
  \begin{equation}
    F_3\left(1+z\right)=c_{3,0}+\frac{c_{3,1}}{10^{c_{3,3}\zeta}+10^{c_{3,4}\zeta}},
    \label{eqn:beta}
  \end{equation}
  where
  \begin{equation}
    \zeta = \log_{10}\left(\frac{1+z}{1+c_{3,2}}\right),
  \end{equation}
  thus resulting in a five-parameter model with parameters $c_{3,i}$.
  The parameters $c_{3,3}$ and $c_{3,4}$ thus determine the low and
  high redshift slopes of this evolution, with a break at redshift
  $c_{3,2}$.  This is similar to the model of
  \citet{2007ApJ...654..731H}, who also favoured a broken power law
  model for the evolution of the faint-end slope of the bolometric
  luminosity function of quasars.  Model 1 thus has 14 parameters.
  Excluding those deemed to be dominated by systematic errors, as
  discussed in the previous section, all of the remaining AGN from
  Table~\ref{tab:samples} are included while fitting this model.

@@

\section{Comparison with other luminosity function determinations}
\label{sec:qlfliterature}
Figure~\ref{fig:params_grand} compares the parameters of the double
power law luminosity function from our analysis of
Section~\ref{sec:bins} to values reported in the literature.  In
general, our break luminosity is brighter and the faint-end slope is
steeper than other determinations.  Note however that several results
from the literature shown in Figure~\ref{fig:params_grand} make
restrictive assumptions while fitting double power law models to data.
For example, \citet{2013ApJ...768..105M} fix the bright-end slope
$\alpha$ to $-4$ at $z=4.7$--$5.1$.  \citet{2016ApJ...833..222J} fix
the faint-end slope $\beta$ to $-2.8$ at $z=5.7$--$6.4$.
\citet{2017ApJ...847L..15O} fix the bright-end slope $\alpha$ to
$-2.8$ at $z=5.5$--$6.5$.  \citet{2015AA...578A..83G} fix the
faint-end slope and the break luminosity in their highest-redshift bin
($z=5.0$--$6.5$).  The choice of data sets is also often different.
For instance, \citet{2015AA...578A..83G} do not include the SDSS
Stripe 82 data from \citet{2013ApJ...768..105M} and the AGN samples of
\citet{2010AJ....139..906W} and \citet{2015ApJ...798...28K} in their
analysis.  (We discuss the results of \citet{2015AA...578A..83G} in
greater detail in Appendix~\ref{sec:conv}.)  Of the remaining
determinations, our parameter values are closest to those reported by
\citet{2016ApJ...829...33Y} at $z=4.7$--$5.4$.

\begin{figure*}
  \begin{center}
    % summary_grand.py
    \includegraphics[width=\textwidth]{evolution_grand.pdf}
  \end{center}
  \caption{A comparison of our inferred double power law parameter
    values with those reported in the literature.  Black points show
    our determinations from Figure~\ref{fig:evoln}.  Blue points show
    other values, from \citet[triangles]{2012ApJ...755..169M},
    \citet[squares]{2016ApJ...833..222J},
    \citet[diamonds]{2011ApJ...728L..26G},
    \citet[crosses]{2013ApJ...768..105M}, \citet[downward
      triangles]{2015AA...578A..83G},
    \citet[pentagons]{2018PASJ...70S..34A}, \citet[leftward
      triangles]{2017ApJ...847L..15O},
    \citet[asterisks]{2016ApJ...829...33Y},
    \citet[circles]{2013ApJ...773...14R},
    \new{\citet[hexagons]{2009MNRAS.399.1755C}} and \citet[rightward
      triangles]{2009A&A...507..781S}.  Where necessary, values from
    the literature have been converted to our cosmology.
    \label{fig:params_grand}}
\end{figure*}

>>>>

\item
  In Model 1 we assume that the functions $F_0$, $F_1$ and $F_2$ from
  Equation~\eqref{eqn:global} are Chebyshev polynomials in
  $\left(1+z\right)$, written as
  \begin{equation}
    F_i\left(1+z\right)=\sum_{j=0}^{n_i}c_{i,j}T_j\left(1+z\right)
    \label{eqn:cbs}
  \end{equation}
  for $i\in\{0,1,2\}$, where $c_{i,j}$ are the parameters from
  Equation~\eqref{eqn:global} and $T_j\left(1+z\right)$ are Chebyshev
  polynomials of the first kind. We try successively higher orders of
  Chebyshev polynomials in order to arrive at a good fit with the
  data.  As we discuss below, we find that $\phi_*$, $M_*$ and
  $\alpha$ prefer quadratic, cubic, and linear evolutions in
  $\left(1+z\right)$, respectively.  For the faint-end slope $\beta$
  we adopt a double power law to account for a possible break at
  $z\sim 3$ that is currently not covered with credible data \new{with
    well-characterised selection function}.  Thus we write
  \begin{equation}
    F_3\left(1+z\right)=c_{3,0}+\frac{c_{3,1}}{10^{c_{3,3}\zeta}+10^{c_{3,4}\zeta}},
    \label{eqn:beta}
  \end{equation}
  where
  \begin{equation}
    \zeta = \log_{10}\left(\frac{1+z}{1+c_{3,2}}\right),
  \end{equation}
  thus resulting in a five-parameter model with parameters $c_{3,i}$.
  The parameters $c_{3,3}$ and $c_{3,4}$ thus determine the low and
  high redshift slopes of this evolution, with a break at redshift
  $c_{3,2}$.  This is similar to the model of
  \citet{2007ApJ...654..731H}, who also favoured a broken power law
  model for the evolution of the faint-end slope of the bolometric
  luminosity function of quasars.  Model 1 thus has 14 parameters.
  Excluding those deemed to be dominated by systematic errors, as
  discussed in the previous section, all of the remaining AGN from
  Table~\ref{tab:samples} are included while fitting this model.

@@

\section{Comparison with other luminosity function determinations}
\label{sec:qlfliterature}
Figure~\ref{fig:params_grand} compares the parameters of the double
power law luminosity function from our analysis of
Section~\ref{sec:bins} to values reported in the literature.
\new{There is significant disagreement between various inferences.
  The break magnitude and the luminosity function amplitudes are
  particularly severely discordant towards the higher-redshift end of
  Figure~\ref{fig:params_grand}, although the disagreement is
  appreciable at other redshifts too.  The slopes are in conflict at
  all redshifts.} In general, our break luminosity is brighter and the
faint-end slope is steeper than other determinations.

Several results from the literature shown in
Figure~\ref{fig:params_grand} make restrictive assumptions while
fitting double power law models to data.  For example,
\citet{2013ApJ...768..105M} fix the bright-end slope $\alpha$ to $-4$
at $z=4.7$--$5.1$.  \citet{2016ApJ...833..222J} fix the faint-end
slope $\beta$ to $-2.8$ at $z=5.7$--$6.4$.
\citet{2017ApJ...847L..15O} fix the bright-end slope $\alpha$ to
$-2.8$ at $z=5.5$--$6.5$.  \citet{2015AA...578A..83G} fix the
faint-end slope and the break luminosity in their highest-redshift bin
($z=5.0$--$6.5$).  \new{This biases the inference of other parameters
  and may also underestimate their uncertainties.}

The choice of data sets is also often different.
For instance, \citet{2015AA...578A..83G} do not include the SDSS
Stripe 82 data from \citet{2013ApJ...768..105M} and the AGN samples of
\citet{2010AJ....139..906W} and \citet{2015ApJ...798...28K} in their
analysis.  (We discuss the results of \citet{2015AA...578A..83G} in
greater detail in Appendix~\ref{sec:conv}.)

\new{The uncertainties reported by \citet{2012ApJ...755..169M} are
  unphysical.  At $z\sim 4$, the uncertainty reported by these authors
  on $\phi_*$ spans negative values.  It is unclear if the double
  power law model was fit to data after binning in magnitude and how
  the uncertainties were derived.  At lower redshifts, our fits to the
  $z<2$ luminosity function have steeper faint ends than those
  reported by \citet{2009MNRAS.399.1755C}.  Upon closer inspection, we
  found that our binned luminosity functions differ systematically
  from those of \citet{2009MNRAS.399.1755C} in one or two faintest
  bins at all redshifts.  Unfortunately, \citet{2009MNRAS.399.1755C}
  do not provide enough detail for us to deduce the causes behind this
  difference, but one possibility is that these authors made specific
  interpolation choices while integrating over the completeness map.
  At intermediate redshifts, some of the parameter values reported
  \citet{2013ApJ...773...14R} also have unphysical uncertainties.
  Uncertainties for these values do not enclose the measurement.
  While our disagreement with \citet{2013ApJ...773...14R} in
  Figure~\ref{fig:params_grand} is relatively minor, we note that this
  is in a redshift range where the data suffer from severe systematic
  errors.  The reason our parameter values disagree with those given
  by \citet{2011ApJ...728L..26G} is also unclear.  The selection
  function provided by these authors had completeness values that
  exceeded 100\%, perhaps due to extrapolation errors.  When this
  happened we assumed 100\% completeness.  \citet{2018PASJ...70S..34A}
  report very flat faint-end slope that is inconsistent with our
  inference at all redshifts.  As discussed in
  Section~\ref{sec:reion}, this could be because of missing AGN faint
  population $M_{1450} > -23.5$ due to point source selection and
  partly also because of photometric redshift errors.  Thus, of the
  five determinations in the literature with unconstrainted double
  power law fits,} our parameter values are closest to those reported
by \citet{2016ApJ...829...33Y} at $z=4.7$--$5.4$.

\new{In sum, Figure~\ref{fig:params_grand} suggests that it is
  incorrect to fix QLF parameters while fitting QLF models and one
  should only fit models if data actually span the magnitude range.
  In order to emphasize this, we have shown inferences without
  errorbars as open symbols.  Note that the formal statistical
  uncertainty of our inferences in often smaller than the symbol size
  in Figure~\ref{fig:params_grand}.}

\begin{figure*}
  \begin{center}
    % summary_grand.py
    \includegraphics[width=\textwidth]{/Users/girish/Desktop/evolution_grand.pdf}
  \end{center}
  \caption{A comparison of our inferred double power law parameter
    values with those reported in the literature.  Yellow points show
    our determinations from Figure~\ref{fig:evoln}.  \new{(Our
      statistical errors are often smaller than the symbol size.)}
    Other data points show values from
    \citet[triangles]{2012ApJ...755..169M},
    \citet[squares]{2016ApJ...833..222J},
    \citet[diamonds]{2011ApJ...728L..26G},
    \citet[crosses]{2013ApJ...768..105M}, \citet[downward
      triangles]{2015AA...578A..83G},
    \citet[pentagons]{2018PASJ...70S..34A}, \citet[leftward
      triangles]{2017ApJ...847L..15O},
    \citet[asterisks]{2016ApJ...829...33Y},
    \citet[circles]{2013ApJ...773...14R},
    \citet[hexagons]{2009MNRAS.399.1755C} and \citet[rightward
      triangles]{2009A&A...507..781S}.  \new{Measurements for which no
      error bars are available are shown using open symbols.}  Where
    necessary, values from the literature have been converted to our
    cosmology.
    \label{fig:params_grand}}
\end{figure*}
